---
title: "Task_4 Web_Scraping"
author: "Abraham. G. Habtai"
date: "8 oktober 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list=ls())
getwd()
setwd("C:/Users/Abraham/Documents/Github/homework-BED-2056")

library(rvest)
library(tidyverse)
library(rlist)
library(plyr)  
```

# Web Scraping

**Specifying the url for desired website to be scrapped**
```{r}
url <-"https://w2.brreg.no/kunngjoring/kombisok.jsp?datoFra=01.01.2018&datoTil=08.10.2018&id_region=100&id_fylke=19&id_kommune=-+-+-&id_niva1=51&id_niva2=-+-+-&id_bransje1=0"
```

**Reading & checking the HTML code from the website**
```{r}
Webpage <- read_html(url)
str(Webpage)
```
**Using CSS selectors to scrap the kunngjorings section**
```{r}
Kunngjorings_Type_html<- html_nodes(Webpage,"p a")
```

**Converting the title data to text**, *and changing class to factor & checking*
```{r}
Kunngjorings_Type <- html_text(Kunngjorings_Type_html)
Kunngjorings_Type<-factor(Kunngjorings_Type)
head(Kunngjorings_Type)
tail(Kunngjorings_Type)
str(Kunngjorings_Type)
```

** Using CSS selectors to scrap the dato section** &

*converting to text* &

*Converting "dato" from charachter to date format*

```{r}
dato1<-html_nodes(Webpage,"tr~ tr+ tr td:nth-child(6) p")
dato<-html_text(dato1)
head(dato)
dato<-as.Date(dato, format = "%d.%m.%Y")
str(dato)

```

**Using CSS selectors to scrap the digits section**. Then converting it to text
```{r}
digits_html<-html_nodes(Webpage,"td:nth-child(4) p")
#converting
digits<-html_text(digits_html)
head(digits)
str(digits)
```

*Data-Preprocessing: removing extra space in digits*
```{r}
digits<-str_replace_all(string= digits, pattern=" ", repl="")
View(digits)
```

*converting from charcter to numeric*. I have skipped this part do to the fact, that the value of the numbers here is to seprate charcters from companies
```{r}
digits<-as.numeric(digits)
View(digits)
str(digits)
head(digits)
```

**Using CSS selectors to scrap the names section**. 

Then converting the html section to text & characters
```{r}
name_html_type<-html_nodes(Webpage,"td td:nth-child(2) p")
name<-html_text(name_html_type[2:274])
name<-as.character(name)
str(name)
```
**creating a dataframe of my vectors**
```{r}
df<-data.frame(name, dato,digits,Kunngjorings_Type, stringsAsFactors = F)
glimpse(df)
View(df)
```
**Selecting companies in Troms county**
```{r}
Bedrift_kungjoringer<-df[grep("AS", df$name),]
str(Bedrift_kungjoringer)
View(Bedrift_kungjoringer)
```
**companies who have been declared compulsory dissolution (Tvangsoppløsning)**
```{r}
Tvangsoppløste_B<-Bedrift_kungjoringer[grep("Tvangsoppløsning", Bedrift_kungjoringer$Kunngjorings_Type),]
str(Tvangsoppløste_B)
View(Tvangsoppløste_B)
```
**ploting "kunngjorings_type" and date**
```{r}
qplot(data = Bedrift_kungjoringer,dato,fill = Kunngjorings_Type, binwidth = 50)
```

**creating frequency data of "kunngjoringer"**
```{r}
Kunngjorings_data<-count(Bedrift_kungjoringer,"Bedrift_kungjoringer$Kunngjorings_Type")
View(Kunngjorings_data)
```



